Response to Reviewers (Revision 1)

### 2020-05-15 ICT_Frontiers_rev202001_reply_rev1.tex

% =================================== Title ================================== %
\title{Response to Reviewers $Rev^1$}
\date{\today}
\author{}

@@

    \maketitle
    \section*{Reply to Editor}
        \begin{question}
        In addition, I have a question. if we view molecules as coarse grains of elementary particles, would the phenomenon of molecular recognition have high NTIC and thus be conscious?
        \end{question}

        \begin{ans}
            Hi Prof. Hoffman,
            Thank you for your attention to our manuscript and your interesting question. \\
            If we understand correctly, molecular recognition refers to specific types of interactions among molecules that form molecular complexes. There is no question that molecular complexes are coarse-grainings of molecules via molecular recognition. Based on our hypothesis, if the dynamics of a molecular complex is an NTIC process, the information closure theory of consciousness (ICT) would claim that the molecular complex has a certain degree of consciousness.
        \end{ans}

@@

    	\begin{ans}
    		\newline
    		a) It is true it is true that the information flow term $J_t(E\rightarrow Y)$ does not have to be zero for $NTIC>0$. However, in Definition 2, a C-process is informationally closed to the microscopic universe process $X$. This implies C-process is also informationally closed to any other coarse-grainings of X including E (see also our reply to Q2). Currently, we only consider closed NTIC processes are C-processes. 
    		Regarding the video camera example, please see more discussion in our reply to your Q6. \\

@@

    		\noindent
    		b) It is true that NTIC is not state-dependent. We agree that state-dependent measurements are essential to describe the dynamics of conscious experience. We are  working on state-dependent formulations for the next version of the ICT. In contrast to the current version, this work involves point-wise informational measures and requires more space and discussion. Therefore, we prefer to address the state-dependent version of ICT in future studies and keep the first version of our theory simple.\\
    		We appreciated that the reviewer pointed this out. We have added a short paragraph about this issue.

	    	\addnew{\lineref{line:r1-state-dep}}{
	    		In this article, we do not use a state-dependent formulation of NTIC. However, we believe that the state-dependent NTIC is essential to describe the dynamics of conscious experience. Therefore, further research using point-wise informational measures to construct state-dependent NTIC is needed for the next version of ICT.}
    	\end{ans}

@@

        \begin{ans}        	
            The C-processes are constructed to answer questions about the scale problem of consciousness. Their definition therefore states their relation to the microscopic scale $X$. 
            At the same time it would be possible to remove $X$ from the definition and instead require that $Y$ is informationally closed with respect to all other processes. In some cases such a definition would be more general than the present one for example when there is no final microscale and instead there is an infinite number of more and more microscopic scales. However, we find the use of an explicit microscale $X$ easier to understand and sufficient to communicate the idea. Note that closure with respect to $X$ (if it exists) implies closure with respect to every coarse-graining of $X$.   
            To see this note that the information transfer from any coarse-graining (including $E$ and $S$) of $X$ to $Y$ must be lower than that from $X$ to $Y$, i.e. $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; S_t|Y_t)$ and $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; E_t|Y_t)$. So that $Y$ is informationally closed with respect to $X$ implies that $Y$ is also informationally closed with respect to $S, E$, and all other coarse-grainings of $X$.
        \end{ans}

@@

        \begin{ans}
            Yes. As mentioned in our answer to Q2 $Y$ being informationally closed with respect to $X$ implies that $Y$ is also informationally closed with respect to E, i.e. $J_t(E\rightarrow Y) = 0$.
            As explained in Question 1a, we currently only consider informationally closed processes as C-processes. The reviewer is also correct that our internal states depends to some degree on unpredictable sensory inputs from the environment. This results in some interesting predictions. For example, the unpredicted sensory inputs may temporally break informational closure and ICT predicts that conscious agents may then lose consciousness for a short time. Unfortunately, referring to your Q1b, the current version of ICT does not include state-dependent IC and NTIC. Therefore, the current formulation of ICT cannot well describe the dynamics of conscious experience under unpredictable states. We expect that our next version of ICT can better answer your question.

@@

            Instead of imposing the exclusion criterion, the concept of informational closure itself already involves the notion of individuality and defining the boundary of a system. \citep{BERTSCHINGER.2006}. This allows ICT to solve the individuality problem of consciousness in some cases (but not all, please see the paragraph in Limitation from Line~\lineref{line:individuality}) without imposing an exclusion criterion. Therefore, it is true that Krakauer's boundary detection procedure can potentially helpful and be adapted for ICT in the future.

@@

            We understand that not solving individuality completely is one major weakness of the current version of ICT (and all IC and NTIC based theories). More work on this issue is needed in our following research.

@@

        \begin{ans}
        	The reviewer is right. We have reconsidered case of the feed-forward networks and the video camera example (which can be considered as a single layer feed-forward network). According to ICT, feed-forward networks can be conscious under for deterministic sensor processes. We thank the reviewer to correct this point. In this case also a video camera can achieve positive levels of NTIC and, therefore, be conscious. We have worked extensively on Section \ref{sec:causality} and Section 5 to make this clear (for Section 5, please see from Line:~\lineref{line:notIC}).
        % 	There we have weakened multiple claims in the original version of the manuscript.
        % 	Concerning the camera example we also show that for a camera system filming an environment for which the mutual information from one step to the next is higher than the mutual information between one camera image (sensor values) and the next there are systems that achieve higher NTIC. 
        % 	For the case of the feedforward network we speculate that a similar situation remains true and that there are always systems that achieve higher levels of consciousness than those consisting only of feedforward networks.
        	In summary, we mainly revised our manuscript as follows:
        	\begin{itemize}
        	    \item Add Section \ref{sec:causality} to illustrate two NTIC scenarios about causality. 
        	    \item Add sensory channels in Fig.~2
        	    \item Extensively modify the paragraphs about feed-forward networks and memory in Section 5
        	    \item Add a session in the Appendix to prove that NTIC achieved by modelling the environment can potentially achieve higher NTIC then the one by copying sensory values (e.g., the video camera).
        	\end{itemize}

@@

    	\begin{ans}
	    	We want to emphasise that not all the processes in the neural system are NTIC processes, since some processes in the neural system are not informationally closed.
	    	To the conscious (NTIC) process, the rest of the neural system is considered as part of the environment. This notion is shortly indicated at line \lineref{line:neu-env} in our first version of the manuscript. These processes are still active during sleep and dreaming. We speculate that, during dreaming, the neural system can stably form the NTIC process with respect to its environment, i.e. other parts of the neural system.  However, at the current stage, this is mere speculation so we restrained ourself from making the statement in our manuscript. However, we thank the reviewer for bringing up this important question. This is also an empirical question that can and should be tested in future studies. We believe that this is still worth mentioning. We have added a short paragraph as follows:

			\addnew{\lineref{line:dream}}{Explaining conscious experience during dreaming is always a challenge to theories of consciousness. ICT currently does not have a certain answer to dreaming. However, we want to emphasise that not all the processes in the neural system are NTIC since some processes are not informationally closed. They mainly passively react to sensory inputs or other processes in the neural system. To the conscious (NTIC) process, the rest of the neural system and the body should be also considered as part of the environment. They retains some degree of activities during sleep and dreaming. We speculate that, during dreaming, the neural system stably forms an NTIC process with respect to its environment, i.e. the other parts of the neural system. However, at the current stage, this is mere speculation. Searching for the NTIC process(es) during dreaming is a important step to extend the scope of ICT in future research.}
    	\end{ans}

@@

    	\begin{ans}
    		\begin{enumerate}
    			\item It's true that we were also confused about it during submission. 
    			We have modified this as follows: \\
    			\textit{"We propose a new theory of consciousness and discuss some preliminary implications."}

@@

    			\item We agree with the reviewer's comment. 
                In fact, we do not differentiate states of processes between activation and relation. Take neural network as an example; the relations between elements are determined by the topology of a network (structure) and its hyperparameters (e.g. activation functions). We agree that activation and relation of a neural network should be both considered. After all, they are all merely the parameters for the process of the neural network. The only difference between the two groups of the parameters is the temporal scales of changes. States of activation may have more rapid dynamics than states of relation. In ICT, the two sets of parameters do not have any qualitative differences.

@@

    \section{Reply to Reviewer 2}
        \begin{question}
			I had a few problems in reading the paper, which I think should be addressed (especially the first) before the paper is published. For detailed notes on these see below.

			\begin{enumerate}
				\item The coarse-graining idea seems undefined in critical ways, but the paper reads as though it is well-defined. So maybe the authors have compressed too much detail? In the formalism presented it is unclear what coarse-graining (or information closure to other grains) amounts to. With this lack of detail, it is then unclear to me why intermediate maxima in IC are a plausible result (why does IC not just decline with progressive coarse graining).

				\item The idea of 'simulation'. This is a more minor point but I would appreciate if the authors could be clearer on this. It is arguable whether or not consciousness simulates anything (e.g. see Hoffman's interface theory); and some of the assertions the authors make re simulation seem unfounded anyways. But it could be that they mean something different or subtle (that consciousness is linked to or represents or etc the environment)

				\item There were several other assertions that stood out to me as strange or wrong, but could be a matter of explanation or ignorance on my part (the feedforward system, the cut-apart system). Either way some more explanation would be good.
			\end{enumerate}
        \end{question}

    	\begin{ans}
    		We thank the reviewer for the critical comments. We have replied these comments in details in the following Q\&A. 
    	\end{ans}

        \begin{question}
			The English is not perfect and needs some good proofreading, though it was understandable throughout.
        \end{question}

    	\begin{ans}
    		We have invited a native English speaker for proofreading. Please inform us if it is still not clear or unreadable. 
    	\end{ans}

    	\begin{question}
			On line 182, defining C-processes as cases where 'Y is informationally closed to X'. This is now information closure in the sense of coarse-graining, but no such thing has been defined yet? Is it supposed to be so trivial that it is not required to make it explicit? To this point, closure is defined entirely in terms of system with respect to environment.

			Basically, I am not sure whether closure between scales is a matter of same-time (e.g. $I(Y_{t+1};X_{t+1})$) or across-time interactions ($I(Y_{t+1};X_t)$). Or could it be both?    		
    	\end{question}

    	\begin{ans}
    		We agree that this point is not clear. Even though the Bayesian graphs for the system-environment dependency are different from the one for the micro-macro level dependency, we apply the same definitions of information flow ($J_{t}(X \rightarrow $Y$ )$) and informational closure ($J_{t}(X \rightarrow $Y$ )=0$) to both graphs.

    % 		This is a critical assumption in ICT because applying the same definition of informational closure in both scenarios can solve the scale problem of consciousness (informational closure from one level to other levels) and construct our hypothesis about the relation between NTIC and consciousness (informational closed from a process to its environment) in an integrated framework.

    % 		In terms of the Bayesian graphs for the micro-macro level dependency and the definition of informational closure between scales, we followed the conventional setting (e.g. \cite{PFANTE.2014}). It is important to note that coarse-graining does not and should not take time $Y_t=f_Y(X_t)$ (also see our Definition 1). Coarse-graining is merely a function which maps microstates of a system to macrostates, and the microstates and the macrostates are only different level of descriptions of the same system.

    % 		We agree that we did not indicate this assumption explicitly and may lead to some confusion for our readers. 
    		We have added a paragraph to make this point explicit.

    		\addnew{\lineref{line:IC2CG}}{
    			Note that, here we applied the same definitions of information flow (Eq.~\ref{eq:InformationFlow}) 
    			\begin{align}
    			    J_{t}(E \rightarrow Y )=I(Y_{t+1};E_t|Y_t)
    			\end{align}
    			to the system-environment dependency and the micro-macro level dependency
                 \begin{align}
    			    J_{t}(X \rightarrow Y )=I(Y_{t+1};X_t|Y_t)
    			\end{align}  
                 even though the Bayesian graphs are different in the two scenarios. Both of these settings have already been used in the literature \citep[see][]{BERTSCHINGER.2006, PFANTE.2014}).
    		}	
    	\end{ans}

    	\begin{question}            
    		On line 241: '.. not sufficiently coarse-grained variables have low values of NTIC', this is phrased as though it is necessarily true (and also that 'we saw above', though I do not see above where this is justified), but is it?

    		At the very finest grain, wouldn't even all the most 'stochastic' dynamics of a system be accounted for by prior states of the system, or by the environment? Why wouldn't we assume that NTIC *only decreases* as the system is coarse-grained (as number of elements/states is decreased), for similar reasons as it must be zero at a 1-element 1-state system as the authors note? This seems an important point to be very clear on\dots
    	\end{question}

    	\begin{ans}
        	We understand that this section in the last version is very unclear. Therefore, to make this point clear, we have added a new paragraph and made a significant revision of this section. In short, we more formally describe how NTIC may change non-monotonically from the finest microscale to the coarsest macroscale. Please see our revised manuscript from Line \lineref{line:non-monotonic} to Line \lineref{line:non-monotonic_end}.
    	\end{ans}

    	\begin{question}
    		on line 263: 'NTIC processes encodes environmental information in its state. This suggests that a NTIC process can be considered as a process that simulates the environmental dynamics.'

    		Why does encoding suggest simulation? An encoding *could* be a simulation, but it could well be nothing like a simulation, if we understand simulation to mean something like an imitation or reconstruction of some structure or dynamics. Two totally different environmental situations could potentially be encoded in exactly the same way (eg. as a string of 1s and 0s).

    		The 'simulation' notion is brought up again in section 5.2 (line 344), citing Bertschinger et al, though I do not find the idea in that paper.. I think authors need to be clearer on what they mean by 'simulation' to make this point.
    	\end{question}

    	\begin{ans}
    		The notion of simulation is the same as the 'Modeling' case on Page 4 in \cite{BERTSCHINGER.2006}: 
    		\begin{quote}
		    	\textit{"B2)~Modeling: The system reaches synchronization and internalizes the correlations observed in the environment by building up own structures."}
    		\end{quote}

    	    To avoid any confusion to our reader, in this revision, we added a new subsection \ref{sec:causality} to describe the scenario of modelling.
    		Also, we replaced "simulation" and "encoding" with "modelling" in many places in this revision. We hope that this change can make our point more clear. 
    	\end{ans}

   	\begin{question}
			line 306: 'Blindsight patients\dots make above chancel-level visual judgments without having any conscious perception about visual stimuli' I am not sure this characterization of blindsight is correct, it may be a matter of the phrasing. It could be - or probably is - the case that 'blindsight' patients always have some conscious experience of what drives their correct responses, but that the 'visual character' of these experiences is degraded or missing.
			(Overgaard, Experimental Brain Research 2011)
			for a specific example
			(Mazzi, Bagattini, Savazzi; Frontiers in Psychology, 2016)
    	\end{question}

   		\begin{ans}
   			Yes, we specifically wanted to address the visual character of their experience. We agree that some patients still preserve some forms of conscious experience. 
   			We have changed our sentence and cited the relevant references as follows:
   			\revise{\lineref{line:r2q6}}
   			{
   				Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements without having any conscious perception about visual stimuli.
   			}
   			{
   				Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements with degraded or missing visual experience. (However, in some cases, they may still preserve some forms of conscious experience, see \cite{overgaard2011visual, mazzi2016blind}.) 
   			}
   		\end{ans}

    	\begin{question}
            on Line 316: On the issue of a feedforward network, the current state of a feedforward network with more than one layer is certainly driven by its own past states! So, mutual information of a feedforward network over a time lag should not be zero, unless I am misunderstanding something here?
			At the same time, I can see a version of the authors' argument here - for a unit in a feedforward network with depth (distance-from-input) of N, a time lag of N time steps would always account fully for the states of the element. Is this the idea?		
    	\end{question}

 		\begin{ans}
 		    The reviewer is correct. As we have now made clear in the case of a deterministic observation process a feedforward network (or a copying process) can be informationally closed and also maintain mutual information such that it is conscious according to ICT. We call such process passive adaptation processes and introduce this in the new section \ref{sec:causality}. We mention the possibility of conscious feedforward networks now in section \ref{sec:reflexive} and add a footnote specific for n-layer feedforward networks at Line \lineref{line:feedforward}. Note that most observation processes in the real world are not deterministic so that most passive adaptation processes aren't conscious.
 		\end{ans}

    	\begin{question}
    		on line 441: under the 'Prediction after system damaged', it is suggested that ICT predicts cutting a system in half would render both halves unconscious. But this would only be the case if neither half contains its own C-processes, yes? Since ICT allows that many C-processes can exist at the same time, it would have to be some special case for this prediction to hold true. So it seems to me the prediction is actually similar to that of IIT.
    	\end{question}

    	\begin{ans}
        	We assume that we have one conscious (NTIC) process involving information in both brain hemispheres. Namely, the process is informationally closed only when we consider the information in both hemispheres. We agree that if both hemispheres have their own NTIC process ICT should predict no change of conscious experience before and after cutting. Cutting should not make any difference because they are informationally closed with respect to each other. We also agree that this prediction is relatively premature. Systematical comparisons between model predictions can be done by rigorous modelling studies in the future. We also weakened our statement by added the following sentence:

        	\addnew{\lineref{line:r2-cutting}}{Nevertheless, this prediction is relatively premature. Systematical comparisons between model predictions can be done by rigorous modelling studies in the future. }

        \begin{question}                              
            Line 540: the theory doesn't really seem to intend to solve the hard problem(s) at all, much less 'completely solve'.            
            I was expecting the problem of dreaming to come up in the last section (maybe along with SMC for which it is a serious problem). When dreaming the information between environment and the system is virtually zero; is this a problem for ICT? Also, more specific phenomena like the eigengrau - if you take away all visual input, for long enough, I do not lose my visual experiences - rather they take on a special state. Does ITC need to accept the possibility that even *trivial* IC can be a conscious process?
        \end{question}

    	\begin{ans}
    		We appreciate the reviewer to bring up the hard problem of consciousness and dreaming. This is a very good question and dreaming really poses a challenge for ICT. At the moment we can only speculate about possible solutions. One point We want to emphasise is that not all the processes in the neural system are NTIC processes. To the conscious (NTIC) process, the rest of the neural system should be considered as part of the environment. This notion is shortly indicated at line \lineref{line:neu-env} in the original manuscript. We speculate that, during dreaming, the neural system can stably form the NTIC process with respect to its environment, i.e. other parts of the neural system. The same idea can be also applied to phenomena like Eigengrau. However, at the current stage, this is mere speculation so we restrained ourself from making the statement in our last version of the manuscript. However, we thank the reviewer for bringing up this important question. We believe that this is still worth mentioning. We have added a short paragraph as follows:

            \addnew{\lineref{line:dream}}{Explaining conscious experience during dreaming is always a challenge to theories of consciousness. ICT currently does not have a certain answer to dreaming. However, we want to emphasise that not all the processes in the neural system are NTIC since some processes are not informationally closed. They mainly passively react to sensory inputs or other processes in the neural system. To the conscious (NTIC) process, the rest of the neural system and the body should be also considered as part of the environment. They retains some degree of activities during sleep and dreaming. We speculate that, during dreaming, the neural system stably forms an NTIC process with respect to its environment, i.e. the other parts of the neural system. However, at the current stage, this is mere speculation. Searching for the NTIC process(es) during dreaming is a important step to extend the scope of ICT in future research.}

    		Finally, we believe that this is a good
    		empirical question that can and should be tested in future studies. 
    	\end{ans}

	\bibliography{ref}
\end{document}

>>>>

% =================================== Title ================================== %
\title{Response to Reviewers (Revision 1)}
\date{\today}
\author{}

@@

    \maketitle

@@

    	\begin{ans}
    		\newline
    		a) It is correct that the information flow term $J_t(E\rightarrow Y)$ does not have to be zero for $NTIC>0$. However, in Definition 2, a C-process is informationally closed to the microscopic universe process $X$. This implies that the C-process is also informationally closed to any other coarse-graining of X, including E (see also our reply to Q2). Currently, we only consider that closed NTIC processes are C-processes. 
    		Regarding the video camera example, please see more discussion in our reply to your Q6. \\

@@

    		\noindent
    		b) It is correct that NTIC is not state-dependent. We agree that state-dependent measurements are essential to describing the dynamics of conscious experience. We are working on state-dependent formulations for the next version of the ICT. In contrast to the present version, this work involves point-wise informational measures and requires more space and discussion. We would therefore prefer to address the state-dependent version of ICT in future studies and keep the first version of our theory simple.

    		Nevertheless, we appreciate that the reviewer’s raising of this issue, and have added a short paragraph about it:

	    	\addnew{\lineref{line:r1-state-dep}}{
	    		In this article, we do not use a state-dependent formulation of NTIC. However, we believe that state-dependent NTIC is essential to describing the dynamics of conscious experience. The next version of ICT therefore requires further research using point-wise informational measures to construct state-dependent NTIC.}
    	\end{ans}

@@

        \begin{ans}        	
            The C-processes are constructed to answer questions about the scale problem of consciousness. Their definition therefore states their relation to the microscopic scale $X$. 
            At the same time it would be possible to remove $X$ from the definition and instead require that $Y$ is informationally closed with respect to all other processes. In some cases such a definition would be more general than the present one for example when there is no final microscale but instead an infinite number of more and more microscopic scales. However, we find the use of an explicit microscale $X$ easier to understand and sufficient to communicate the idea. Note that closure with respect to $X$ (if it exists) implies closure with respect to every coarse-graining of $X$.   
            To grasp this, note that the information transfer from any coarse-graining (including $E$ and $S$) of $X$ to $Y$ must be lower than that from $X$ to $Y$, i.e. $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; S_t|Y_t)$ and $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; E_t|Y_t)$. Accordingly, $Y$ is informationally closed with respect to $X$ implies that $Y$ is also informationally closed with respect to $S, E$, and all other coarse-grainings of $X$.
        \end{ans}

@@

        \begin{ans}
            Yes. As mentioned in our answer to Q2 $Y$ being informationally closed with respect to $X$ implies that $Y$ is also informationally closed with respect to E, i.e. $J_t(E\rightarrow Y) = 0$.
            As explained in Question 1a, we currently only consider informationally closed processes as C-processes. The reviewer is also correct that our internal states depends to some degree on unpredictable sensory inputs from the environment. This results in some interesting predictions. For example, unpredicted sensory inputs may temporally break informational closure and ICT predicts that conscious agents may then lose consciousness for a short time. Unfortunately, referring to your Q1b, the current version of ICT does not include state-dependent IC and NTIC. Therefore, the current formulation of ICT cannot well describe the dynamics of conscious experience under unpredictable states. We expect that our next version of ICT will be better able to answer your question.

@@

            Instead of imposing the exclusion criterion, the concept of informational closure itself already involves the notion of individuality and defining the boundary of a system. \citep{BERTSCHINGER.2006}. This allows ICT to solve the individuality problem of consciousness in some cases (but not all; please see the paragraph in Limitations from Line~\lineref{line:individuality}) without imposing an exclusion criterion. Therefore, it is true that Krakauer's boundary detection procedure is potentially helpful and can be adapted for ICT in the future.

@@

            We understand that not solving individuality completely is a major weakness of the current version of ICT (and in fact of all IC- and NTIC-based theories). More work on this issue is needed in our future research.

@@

        \begin{ans}
        	The reviewer is correct. We have reconsidered the case of the feed-forward networks and the video camera example (which can be considered as a single-layer feed-forward network). According to ICT, feed-forward networks can be conscious for deterministic sensor processes. We thank the reviewer for correcting this point. In this case also, a video camera can achieve positive levels of NTIC and, therefore, be conscious. We have worked extensively on Sec.~\ref{sec:causality} and Sec.~\ref{sec:reflexive} to make this clear. In summary, we have mainly revised our manuscript as follows:

        % 	There we have weakened multiple claims in the original version of the manuscript.
        % 	Concerning the camera example we also show that for a camera system filming an environment for which the mutual information from one step to the next is higher than the mutual information between one camera image (sensor values) and the next there are systems that achieve higher NTIC. 
        % 	For the case of the feedforward network we speculate that a similar situation remains true and that there are always systems that achieve higher levels of consciousness than those consisting only of feedforward networks.
        	In summary, we mainly revised our manuscript as follows:
        	\begin{itemize}
        	    \item Added Section \ref{sec:causality} to illustrate two NTIC scenarios about causality. 
        	    \item Added sensory channels in Fig.~2
        	    \item Extensively modified the paragraphs about feed-forward networks and memory in Section 5
        	    \item Added a session in the Appendix to prove that NTIC achieved by modelling the environment can potentially achieve higher NTIC than the one which copies sensory values (e.g., the video camera).
        	\end{itemize}

@@

    	\begin{ans}
	    	We want to emphasise that not all processes in the neural system are NTIC processes, since some processes in the neural system are not informationally closed.
	    	To the conscious (NTIC) process, the rest of the neural system is considered as part of the environment. This notion is briefly indicated at line \lineref{line:neu-env} in our first version of the manuscript. These processes are still active during sleep and dreaming. We speculate that, during dreaming, the neural system can stably form the NTIC process with respect to its environment, i.e. other parts of the neural system. At present, however, this is mere speculation so we restrained ourself from making the statement in our manuscript. However, we refrained the reviewer for bringing up this important question. This is also an empirical question that can and should be tested in future studies. We believe that this is still worth mentioning. We have added a short paragraph as follows:

			\addnew{\lineref{line:dream}}{
			Explaining conscious experience during dreaming is always a challenge to theories of consciousness. ICT currently does not have a specific answer to dreaming. However, we wish to emphasize that not all processes in the neural system are NTIC since some processes are not informationally closed. They mainly passively react to sensory inputs or other processes in the neural system. To the conscious (NTIC) process, the rest of the neural system and the body should also be considered as part of the environment. They retain some degree of activity during sleep and dreaming. We speculate that, during dreaming, the neural system stably forms an NTIC process with respect to its environment, i.e. the other parts of the neural system. At present, however, this remains mere speculation. Identification of the NTIC process(es) during dreaming is an important milestone in extending the scope of ICT.}
    	\end{ans}

@@

    	\begin{ans}
    		\begin{enumerate}
    			\item In fact we were also confused about this during submission. 
    			We have modified this as follows: \\
    			\textit{"We propose a new theory of consciousness and discuss some preliminary implications."}

@@

    			\item We agree with the reviewer’s comment. In fact, we do not differentiate states of processes between activation and relation. To take neural networks as an example; : the relations between elements are is determined by the topology of a the network (structure) and its hyperparameters (e.g. activation functions). We agree that the activation and relation of a neural network should be both be considered. After all, they are all of them merely the parameters for the process of the neural network. The only difference between the two groups of the parameters is the temporal scales of changes. States of activation may have more rapid dynamics than states of relation. In ICT, the two sets of parameters do not have any qualitative differences.

@@

\end{document}
